Borel regularity for ODEs and thimble integrals \\ \textbf{[DRAFT]}

### 2023-07-20 draft--Tu.tex

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{eqnarray}
\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
\usepackage{bm} %% for putting series names in bold
%%\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{xparse}
\usepackage{enumitem}
%\usepackage{eqnarray}
%% colors
\usepackage[svgnames]{xcolor}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}

@@

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{rotating}
\newcommand*{\isoarrow}[1]{\arrow[#1,"\rotatebox{90}{\(\sim\)}"
]}

@@

\title{Borel regularity for ODEs and thimble integrals}
\author{Veronica Fantini and Aaron Fenyes}

@@

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
\begin{equation}
e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples. As another example, you might rewrite the integral
\color{DodgerBlue}
\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
\color{black}
\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
as
% see expansion.sage
\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
\color{DodgerBlue}
\begin{align*}
& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
\end{align*}
\color{black}

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. \textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
\end{defn}
\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$. It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

@@

%\color{gray}
%\begin{itemize}
%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
%\begin{itemize}
%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
%\item Feynman diagram series?
%\end{itemize}
%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
%\begin{itemize}
%\item \done{Borel summation work in three steps. First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
%\item {[Draw the square!]}
%\end{itemize}
%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
%\item In many cases, it picks correctly, producing an actual solution to your problem.
%\begin{itemize}
%\item The question of how that happens is the starting point for this paper.
%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$. For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
%\end{itemize}
%\end{itemize}
%\color{black}
\subsection{A new perspective: Borel regularity}
\subsubsection{Introducing Borel regularity}
\begin{itemize}
\item Start instead with a holomorphic solution $\Phi$.
\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
\end{itemize}
\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}

@@

Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization. We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged. In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
\subsubsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).

Watson's theorem was soon improved by Nevanlinna (see a modern proof in Nikolaev, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15), and improved again later by Sokal (Sokal, ``An improvement of Watson's theorem on Borel summability''). These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Definition~5.5]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type.

@@

First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).

@@

\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}. Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

@@

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{eqnarray}
\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
\usepackage{bm} %% for putting series names in bold
%%\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{xparse}
\usepackage{enumitem}
%\usepackage{eqnarray}
%% colors
\usepackage[svgnames]{xcolor}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\let\Im\relax
\DeclareMathOperator{\Im}{Im}

@@

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{rotating}
\newcommand*{\isoarrow}[1]{\arrow[#1,"\rotatebox{90}{\(\sim\)}"
]}

@@

\title{Borel regularity for ODEs and thimble integrals \\ \textbf{[DRAFT]}}
\author{Veronica Fantini and Aaron Fenyes}

@@

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
\begin{equation}
e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples. As another example, you might rewrite the integral
\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
as
% see expansion.sage
\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. \textcolor{orange}{[Nikita has a complementary picture where the position domain is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function \textcolor{orange}{that vanishes at $\infty$ [if it vanishes at $\infty$ it sent to zero, so why this assumption?]} to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).
\end{defn}
\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$. It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

@@

%\color{gray}
%\begin{itemize}
%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
%\begin{itemize}
%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
%\item Feynman diagram series?
%\end{itemize}
%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
%\begin{itemize}
%\item \done{Borel summation work in three steps. First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
%\item {[Draw the square!]}
%\end{itemize}
%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
%\item In many cases, it picks correctly, producing an actual solution to your problem.
%\begin{itemize}
%\item The question of how that happens is the starting point for this paper.
%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$. For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
%\end{itemize}
%\end{itemize}
%\color{black}
\subsection{A new perspective: Borel regularity}
\subsubsection{Introducing Borel regularity}
\begin{itemize}
\item Start instead with a holomorphic solution $\Phi$.
\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
\end{itemize}
%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}

@@

Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization. We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged. In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
\subsubsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite{watson} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite{nikolaev2023exact} Theorem~B.15 and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e. $|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).

@@

First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).

@@

\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{A function $f$ is of exponential type if $|f(z)|\leq C e^{-a|z|}$ for $C,a>0$. Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}. Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

@@

\subsubsection{Why does Borel resummation work for thimble integrals?}
Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $\alpha_1,...,\alpha_N$ \footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
